An antibody-escape calculator for mutations to the SARS-CoV-2 receptor-binding domain

### 2021-12-04 paper/paper.tex
plot variants

\begin{SCfigure*}[][]
\includegraphics[width=0.7\textwidth]{../results/neut_studies/neut_studies.png}
\caption{Correlation of antibody binding scores from the escape calculator with experimentally measured fold changes in neutralization IC50 values for SARS-CoV-2 variants and mutants.
The experimental data of \citet{lucas2021impact} was generated using live virus and sera from vaccinated individuals who were (top) or were not (bottom) previously infected with SARS-CoV-2.
The experimental data of \citet{uriu2021neutralization} and \citet{wang2021antibody} was generated using pseudovirus against convalescent (top) or vaccine (bottom) sera, with the vaccine sera from the Pfizer BNT162b2 or Moderna mRNA-1273 vaccines, respectively. 
The plotted fold changes in neutralization represent the geometric means over all subjects in each cohort.
}
\label{fig:neut_studies}
\end{SCfigure*}

>>>>

\begin{SCfigure*}[][]
\includegraphics[width=0.7\textwidth]{../results/neut_studies/neut_studies.png}
\caption{Correlation of escape scores from the calculator with experimentally measured fold changes in neutralization IC50 values for SARS-CoV-2 variants and mutants.
The experimental data of \citet{lucas2021impact} was generated using live virus and sera from vaccinated individuals who were (top) or were not (bottom) previously infected with SARS-CoV-2.
The experimental data of \citet{uriu2021neutralization} and \citet{wang2021antibody} was generated using pseudovirus against convalescent (top) or vaccine (bottom) sera, with the vaccine sera from the Pfizer BNT162b2 or Moderna mRNA-1273 vaccines, respectively. 
The plotted fold changes in neutralization represent the geometric means over all subjects in each cohort.
}
\label{fig:neut_studies}
\end{SCfigure*}
